---
title: "Getting started with dieroller"
author: "Keqin Cao"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to dieroller}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(dieroller)
```

## Die Rolling
The package `"dieroller"` is a minimal implementation for simulating rolling a die given number of times, and to visualize the relative frequencies in such a series of rolls with a barplot. In addition, there are other methods like extraction, and increment.

## Creating a `die`
The first step is to create a "die" object with the function die():
```{r}
mydie<- die()
mydie
```
By default, die() creates a _fair_ die with standard sides `1`,`2`,`3`,`4`,`5`, and `6`, and with the probability values for each side of 1/6.

You can change the defaults with arguments `sides` and `prob`:
```{r}
loaded<- die(sides = c(1,2,3,4,5,6), prob = c(0.1,0.1,0.1,0.1,0.1,0.5))
loaded
```

## Rolling a die
Once you have defined a `"die"` object, you can use the function `"roll"` to _roll_ a die at a given number of `times`. The output will be an object of class 
`"roll"`, which will contain the vector of `rolls`:
```{r}
roll100<- roll(mydie, times = 100)
roll100
```

The `summary()` function gives you a nice table of frequencies with side, count, and prop:
```{r}
summary(roll100)
```

##Plot of relative frequencies
You can use the function `plot()` to create a graph(barplot) which the relative frequencies of a series of die rolls:
```{r, fig.show="hold"}
plot(roll100)
```

#Addition method of roll
In addition to the basic functions , there are some additional methods you can use to make addition, replacenment, and extraction
```{r}
# roll fair die
set.seed(123)
fair_die <- die()
fair500 <- roll(fair_die, times = 500)
# summary method
summary(fair500)
# extracting roll in position 500
fair500[500]
# replacing last roll
fair500[500] <- 1
fair500[500]
summary(fair500)
# adding 100 rolls
set.seed(123)
fair600 <- fair500 + 100
fair600[500] <- 1
summary(fair600)
```


